An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-06-04 poly-embed-journal/poly-embed-journal.tex
meeting notes

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Minimum Representative Sets, Non-redundancy, and Tight Embeddings}
\label{sec:min-rep-sets}

@@

\begin{corollary}\label{cor:tight-embed-min-rep}
  If $\R$ is a minimum representative set for $L$, then $L$ tightly embeds $L|_\R$.
\end{corollary}
Tightly embedding the restricted loss seems to make embedding construction slightly easier.
While $L|_\R$ is not always the target loss of interest, there should now be a \emph{bijection} from $\R$ to the target reports.
While an embedding only has to be constructed once and is considered an offline computation, its construction might be made easier by a tight embedding.

@@

\begin{corollary}\label{prop:trim-loss-condition}
  Given an loss $L : \R \to \reals^\Y_+$ with finite minimum representative set $\R^*$, we have $\trimcover(L) = \{L(u) \mid u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\} =: \trimnonred(L)$. \jessie{rename with $\trimnonred$ etc.}
\end{corollary}
\begin{proof}[Sketch]
  Let $\U := \{u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$.
  The only time $\U$ contains redundant elements is if there is $u,u' \in \U$ so that $\Gamma_u = \Gamma_{u'}$.  In such a case, removing duplicate elements of $\U$ to form $\U^*$ means $\{L(u) \mid u \in \U\} = \{L(u) \mid u \in \U^*\}$ and $L|_{U'}\}$ is nonredundant, and therefore $\U^*$ is a minimum representative set by Proposition~\ref{prop:tfae-min-rep-nonredundant}, and therefore equal to $\trim(L)$.

@@

\begin{proposition}\label{prop:embed-iff-trims-equal}
  Let the discrete loss $\ell$ be given.
  $L$ embeds $\ell$ if and only if $\trim(L) = \trim(\ell)$.
  Moreover, when $\trim(L) = \trim(\ell)$, given any finite minimum representative set $\R^*$ for $\ell$, we have $L$ tightly embeds $\ell|_{\R^*}$. \jessie{Wanted to add this in meeting 06 May 21, but statement is kinda ugly.}
\end{proposition}
Suppose $\gamma := \prop{\ell}$ and $\Gamma := \prop{L}$, and $\R$ a minimum representative set for $\ell$.
\begin{proof}[Sketch]
  $\implies$
  The optimality condition of embedding means $\Gamma_{\varphi(r)} = \gamma_r$ for all $r \in \R$.
  $\R$ a minimum representative set for $\ell$ then implies $\varphi(\R)$ is a minimum representative set for $L$.
  By Proposition~\ref{prop:trim-unique}, we have
  \begin{equation*}
    \trim(L) = \trim(L|_{\varphi(\R)}) = \trim(\ell|_\R) = \trim(\ell)~.~
  \end{equation*}
  The outside equalities follow from the sets being minimum representative sets, and the middle one follows from the embedding definition since losses have to match at embedded points.

@@

  Finally, consider that $\trim(L) = \trim(\ell)$ implies $L$ embeds $\ell$, and if $\R^*$ is a minimum representative set for $\ell$ then $\trim(L) = \trim(\ell) = \trim(\ell|_{\R^*})$ so $L$ tightly embeds $\ell|_{\R^*}$ by Corollary~\ref{cor:tight-embed-min-rep} and composing the embeddings.
  % and $\ell|_{\R^*}$ is non-redundant by Proposition~\ref{prop:tfae-min-rep-nonredundant}.
  Therefore, $L$ tightly embeds $\ell|_{\R^*}$.
\end{proof}

As we define one loss embedding another, one can imagine an analogous definition where one property embeds another (Definition~\ref{def:prop-embed}), and we can define $\trim(\Gamma)$ as the set of level sets generated by a minimum representative set (Definition~\ref{def:trim-prop}).
See \S~\ref{app:embed-props} for precise definitions and discussion.
Even when using the language of properties, similar results to those above hold; for intuition, the level sets of a property correspond to the subgradients of the Bayes risk of the loss eliciting it.
Since embedding also means matching Bayes risks, the $\trim$s matching follows since the subgradients also trivially match.

We now state a useful result for proving the existence of an embedding loss, which shows remarkable structure of embeddable properties, and the properties that embed them.
First, we conclude that any embeddable property must be elicitable.
We also conclude that if $\Gamma$ embeds $\gamma$, the level sets of $\Gamma$ must all be redundant relative to $\gamma$.
In other words, $\Gamma$ is exactly the property $\gamma$, just with other reports filling in the gaps between the embedded reports of $\gamma$.
(When working with convex losses, these extra reports are typically the convex hull of the embedded reports.)
In this sense, we can regard embedding as only a slight departure from direct elicitation: if a loss $L$ elicits $\Gamma$ which embeds $\gamma$, we can think of $L$ as essentially eliciting $\gamma$ itself.
Finally, we have an important converse: if $\Gamma$ has finitely many full-dimensional level sets, or if $\trim(\Gamma)$ is finite, then $\Gamma$ must embed some finite elicitable property with those same level sets.

\begin{restatable}{proposition}{embedtrim}\label{prop:embed-trim}
	Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
	The following are equivalent:
	\begin{enumerate}\setlength{\itemsep}{0pt}
		\item $\Gamma$ embeds a finite property $\gamma:\simplex \toto \R$.
		\item $\trimnonred(\Gamma)$ is a finite set, and $\cup\,\trimnonred(\Gamma) = \simplex$.
		\item There is a finite minimum representative set $\U$ for $\Gamma$.
		\item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \simplex$.
	\end{enumerate}
	% \raft{I see why you wanted this addition here, but (a) it's clear from the def of embedding, and (b) we don't have varphi defined.  So let's leave it out.}
	Moreover, when any of the above hold, $\trimnonred(\gamma) = \trimnonred(\Gamma) = \{\Gamma_u : u\in\U\} = \Theta$, and $\gamma$ is elicitable.\jessiet{At the moment, don't show anything about $\gamma$ elicitable.}\jessiet{Also, should this statement be $\trimcover(\gamma) = \trimnonred(\gamma) = \trimcover(\Gamma) = \trimnonred(\Gamma) = \{\Gamma_u \mid u \in \U\} = \Theta$? But also, can we pull it out into its own statement? It should follow as a corollary of this and an analogous version of Prop 6.}
\end{restatable}
\begin{proof}
	\jessie{Keep plus example in mind}
	\jessie{Use trim nonredundant and trim covering macros}
	\jessie{1 -> 2 -> 3 -> 1, 3 <=> 4}
	Let $L$ elicit $\Gamma$.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Minimum Representative Sets and Non-redundancy}
\label{sec:min-rep-sets}

@@

\begin{corollary}\label{cor:tight-embed-min-rep}
  If $\R$ is a finite minimum representative set for $L$, then $L$ tightly embeds $L|_\R$. \raf{Changing def tight embed though...}
\end{corollary}
Tightly embedding the restricted loss seems to make embedding construction slightly easier.
While $L|_\R$ is not always the target loss of interest, there should now be a \emph{bijection} from $\R$ to the target reports.
While an embedding only has to be constructed once and is considered an offline computation, its construction might be made easier by a tight embedding.

@@

\begin{corollary}\label{prop:trim-loss-condition}
  Given an loss $L : \R \to \reals^\Y_+$ with finite minimum representative set $\R^*$, we have $\trimcover(L) = \{L(u) \mid u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\} =: \trimnonred(L)$. \jessie{rename with $\trimnonred$ etc.}
\end{corollary}
\begin{proof}[Sketch]
  Let $\U := \{u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$.
  The only time $\U$ contains redundant elements is if there is $u,u' \in \U$ so that $\Gamma_u = \Gamma_{u'}$.  In such a case, removing duplicate elements of $\U$ to form $\U^*$ means $\{L(u) \mid u \in \U\} = \{L(u) \mid u \in \U^*\}$ and $L|_{U'}\}$ is nonredundant, and therefore $\U^*$ is a minimum representative set by Proposition~\ref{prop:tfae-min-rep-nonredundant}, and therefore equal to $\trimcover(L)$.

@@

\begin{proposition}\label{prop:embed-iff-trims-equal}
  Let the discrete loss $\ell$ be given.
  $L$ embeds $\ell$ if and only if $\trimcover(L) = \trimcover(\ell)$.
  Moreover, when $\trimcover(L) = \trimcover(\ell)$, given any finite minimum representative set $\R^*$ for $\ell$, we have $L$ tightly embeds $\ell|_{\R^*}$. \jessie{Wanted to add this in meeting 06 May 21, but statement is kinda ugly.}
\end{proposition}
Suppose $\gamma := \prop{\ell}$ and $\Gamma := \prop{L}$, and $\R$ a minimum representative set for $\ell$.
\begin{proof}[Sketch]
  $\implies$
  The optimality condition of embedding means $\Gamma_{\varphi(r)} = \gamma_r$ for all $r \in \R$.
  $\R$ a minimum representative set for $\ell$ then implies $\varphi(\R)$ is a minimum representative set for $L$.
  By Proposition~\ref{prop:trim-unique}, we have
  \begin{equation*}
    \trimcover(L) = \trimcover(L|_{\varphi(\R)}) = \trimcover(\ell|_\R) = \trimcover(\ell)~.~
  \end{equation*}
  The outside equalities follow from the sets being minimum representative sets, and the middle one follows from the embedding definition since losses have to match at embedded points.

@@

  Finally, consider that $\trimcover(L) = \trimcover(\ell)$ implies $L$ embeds $\ell$, and if $\R^*$ is a minimum representative set for $\ell$ then $\trimcover(L) = \trimcover(\ell) = \trimcover(\ell|_{\R^*})$ so $L$ tightly embeds $\ell|_{\R^*}$ by Corollary~\ref{cor:tight-embed-min-rep} and composing the embeddings.
  % and $\ell|_{\R^*}$ is non-redundant by Proposition~\ref{prop:tfae-min-rep-nonredundant}.
  Therefore, $L$ tightly embeds $\ell|_{\R^*}$.
\end{proof}

As we define one loss embedding another, one can imagine an analogous definition where one property embeds another (Definition~\ref{def:prop-embed}), and we can define $\trimnonred(\Gamma)$ as the set of level sets generated by a minimum representative set (Definition~\ref{def:trim-prop}).
See \S~\ref{app:embed-props} for precise definitions and discussion.
Even when using the language of properties, similar results to those above hold; for intuition, the level sets of a property correspond to the subgradients of the Bayes risk of the loss eliciting it.
Since embedding also means matching Bayes risks, the matching of $\trimnonred$ follows since the subgradients also trivially match.

We now state a useful result for proving the existence of an embedding loss, which shows remarkable structure of embeddable properties, and the properties that embed them.
First, we conclude that any embeddable property must be elicitable.
We also conclude that if $\Gamma$ embeds $\gamma$, the level sets of $\Gamma$ must all be redundant relative to $\gamma$.
In other words, $\Gamma$ is exactly the property $\gamma$, just with other reports filling in the gaps between the embedded reports of $\gamma$.
(When working with convex losses, these extra reports are typically the convex hull of the embedded reports.)
In this sense, we can regard embedding as only a slight departure from direct elicitation: if a loss $L$ elicits $\Gamma$ which embeds $\gamma$, we can think of $L$ as essentially eliciting $\gamma$ itself.
Finally, we have an important converse: if $\Gamma$ has finitely many full-dimensional level sets, or if $\trimnonred(\Gamma)$ is finite, then $\Gamma$ must embed some finite elicitable property with those same level sets.

\raf{NOTES 6/4/2021}

Defining $\trimnonred(\Gamma)$... say $L$ elicits $\Gamma$
\begin{itemize}
\item Define $u \equiv u'$ if $\Gamma_u = \Gamma_{u'}$
\item $\U_\equiv := \{[u] \mid u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$.
\item $\trimnonred(\Gamma):\simplex \toto \U_\equiv$ where $\trimnonred(\Gamma)_{[u]} := \Gamma_u$, i.e., $\trimnonred(\Gamma)(p) = \{[u] \mid u \in \Gamma(p)\}$. 
\item $\trimnonred(L):\U_\equiv\to\reals^\Y_+$ where $L([u]) = L(u)$.  \raf{But well-defined?}
\end{itemize} 
\raf{END NOTES}

\begin{restatable}{proposition}{embedtrim}\label{prop:embed-trim}
	Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
	The following are equivalent:
	\begin{enumerate}\setlength{\itemsep}{0pt}
		\item $\Gamma$ embeds a finite property $\gamma:\simplex \toto \R$.
		\item $\trimnonred(\Gamma)$ is a finite set, and $\cup\,\trimnonred(\Gamma) = \simplex$.
		\item There is a finite minimum representative set $\U$ for $\Gamma$. \raf{$\trimcover(\Gamma)$ is a finite set (but this is by definition currently)}
		\item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \simplex$.
	\end{enumerate}
	% \raft{I see why you wanted this addition here, but (a) it's clear from the def of embedding, and (b) we don't have varphi defined.  So let's leave it out.}
	Moreover, when any of the above hold, $\trimnonred(\gamma) = \trimnonred(\Gamma) = \{\Gamma_u : u\in\U\} = \Theta$, and $\gamma$ is elicitable.\jessiet{At the moment, don't show anything about $\gamma$ elicitable.}\jessiet{Also, should this statement be $\trimcover(\gamma) = \trimnonred(\gamma) = \trimcover(\Gamma) = \trimnonred(\Gamma) = \{\Gamma_u \mid u \in \U\} = \Theta$? But also, can we pull it out into its own statement? It should follow as a corollary of this and an analogous version of Prop 6.}
\end{restatable}
\begin{proof}
	\jessie{Keep plus example in mind}
	\jessie{Use trim nonredundant and trim covering macros}
	\jessie{1 -> 2 -> 3 -> 1, 3 <=> 4}
	Let $L$ elicit $\Gamma$.
